### 2021-03-23 Chapter-2/Chapter-2.tex
Updates from Overleaf

For example, cached
side-channels~\cite{yarom2017cachebleed,191010,184415,Osvik2006,liu2015last,184415}
rely on the time difference between cache misses and cache hits. We introduce two
common attack strategies, namely Prime+Probe~\cite{liu2015last} and
Flush+Reload~\cite{184415}. Prime+Probe targets a single cache set. An
attacker preloads the cache set with its own data and waits until the victim
executes the program. If the victim accesses the cache set and evicts part of
the data, the attacker will experience a slow measurement. 
While Flush+Reload targets a
single cache line, it requires the attacker and victim share some memory. 
During the ``flush'' stage, the attacker flushes the ``monitored
memory'' from the cache and waits for the victim to access the memory,
who will load the sensitive information to the cache line. In the next phase,
the attacker reloads the ``monitored memory''. By measuring the time difference
brought by cache hit and miss, the attacker can further infer the sensitive information.
Some other types of side-channels target different hardware
layers other than CPU cache. For example, the controlled-channel
attack~\cite{7163052}, where an attacker works in the kernel space, can infer
sensitive data in shielding systems by observing the page fault sequences
after restricting some code and data pages.

@@

In this dissertation, we consider three types of granularity: byte (1 Byte), cache line size (64 Bytes), page size (4 KBs). To the best of our knowledge, the three types of granularities can cover most of the side-channel attacks in literature.

\subsection{Cache-level Channel}
Cache-based channels rely on the time difference between cache misses and cache hits. Cache channel attacks can observe cache accesses at the level of cache sets, cache lines or other granularities. 
We introduce two common attack strategies, namely Prime+Probe and
Flush+Reload. Prime+Probe targets a single cache set. An
attacker preloads the cache set with its own data and waits until the victim
executes the program. If the victim accesses the cache set and evicts part of
the data, the attacker will experience a slow measurement. 
While Flush+Reload targets a single cache line, it requires the attacker and victim share some memory. During the ``flush'' stage, the attacker flushes the ``monitored
memory'' from the cache and waits for the victim to access the memory,
who will load the sensitive information to the cache line. In the next phase,
the attacker reloads the ``monitored memory''. By measuring the time difference
brought by cache hit and miss, the attacker can further infer the sensitive information. Some other types of side-channels target different hardware
layers other than CPU cache.

>>>>

\subsection{Cache-level Channel}
Cache channels~\cite{yarom2017cachebleed,191010,184415,Osvik2006,liu2015last,184415} rely on the time difference between cache misses and cache hits. Cache channel attacks can observe cache accesses at the level of cache sets, cache lines or other granularities. 
We introduce two common attack strategies, namely Prime+Probe and
Flush+Reload. Prime+Probe targets a single cache set. An
attacker preloads the cache set with its own data and waits until the victim
executes the program. If the victim accesses the cache set and evicts part of
the data, the attacker will experience a slow measurement. 
While Flush+Reload targets a single cache line, it requires the attacker and victim share some memory. During the ``flush'' stage, the attacker flushes the ``monitored
memory'' from the cache and waits for the victim to access the memory,
who will load the sensitive information to the cache line. In the next phase,
the attacker reloads the ``monitored memory''. By measuring the time difference
brought by cache hit and miss, the attacker can further infer the sensitive information. Some other types of side-channels target different hardware
layers other than CPU cache.

@@
